Compare pseqs

### 2019-05-20 comparepseqs.Rmd
dset to pseq

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(dset) %>%
        mutate(diversities_shannon = scale(diversities_shannon))

>>>>

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(pseq) %>%
        mutate(diversities_shannon = scale(diversities_shannon))
